Dependent Object Types

### 2012-08-31 doc/candidacy/report.tex
def contractiveness

A class template $\cls{x: S \sep \tup d}$ is closely related to a
translucent sum, except that it needs to be instantiated into an
object while a translucent sum is a module. Like in a translucent sum,
$\tup d$ binds term labels to values and type labels to types. The $x$
of type $S$ stands for the self, i.e.\ the object being constructed
from the template. Its scope is the bindings $\tup d$. Since the self
is explicitly typed, the bindings in class templates can contractively
refer to each other (and even to themselves) via $x$, while recall
that, in translucent sums, only later fields can depend on earlier
ones.

>>>>

A class template $\cls{x: S \sep \tup d}$ is closely related to a
translucent sum, except that it needs to be instantiated into an
object while a translucent sum is a module. Like in a translucent sum,
$\tup d$ binds term labels to values and type labels to types. The $x$
of type $S$ stands for the self, i.e.\ the object being constructed
from the template. Its scope is the bindings $\tup d$. Since the self
is explicitly typed, the bindings in class templates can
``contractively'' refer to each other (and even to themselves) via
$x$, while recall that, in translucent sums, only later fields can
refer to earlier ones but the references don't have any
``contractive'' restrictions. Roughly, ``contractiveness'' in
${\nu}Obj$ guarantees that a field cannot be referenced before it is
initalized.
